\vspace{-2cm} Government websites as data: A methodological pipeline for collection, processing, and text analysis

### 2018-01-02 paper/manuscript.tex
finished revisions for SPSA

A local government's website is a standard and general source of information for citizens and other community stakeholders. Accordingly, government websites have become prominent sources of data for a variety of research agendas in public administration, public policy, and political science. Existing research has relied on manual methods of website data collection of processing. Reliance on manual collection and processing limits the scale and scope of website content analysis.  We develop a methodological pipeline that researchers can followed in order to gather, process, and analyze website content with established text analysis techniques. First, for the acquisition of website data, we cover approaches to automated scraping methods. Second, pre-processing is a particularly vital step in text analysis, but when websites are concerned, additional measures need to be taken in order to guard against potential sources of bias. We propose a new method for dealing with the kind of duplicated content that is commonly found in government websites. Finally, we illustrate methods of text analysis using automatically gathered and pre-processed website content. We illustrate our methodological pipeline through a new and innovative dataset---the websites of local governments in Indiana and Louisiana. We build upon recent research that analyzes how change and variation in the partisan control of government relates to content made available on the government's website. We explore the association between mayoral partisanship and the content of city websites.
%\noindent We explore the effect of transitions of power in municipal governments on the content of their websites. We hypothesize that when party control changes, city administrators modify the contents of their websites in order to fit the agenda of the new incumbent. To test this theory, we study cities in Indiana and Louisiana, two states in which all municipal elections are partisan and the parties of the candidates appear on the ballots. Snapshots of websites before and after transitions of power are acquired through the Wayback Machine. We apply statistical topic models based in latent dirichlet allocation, focusing on changes to the websites. We present results on both which topics see the greatest degree of change associated with transitions in city administrations, and how the topics modified differ with regard to political parties.

@@

\section{Background: The Study of Government Websites}

\cite{grimmelikhuijsen2010transparency} run an experiment in which citizens are exposed to randomly selected levels of information about local government council minutes. They find a negative relationship between the information level and perceptions of competence in the local government. This raises an interesting question regarding whether citizens or more likely to participate when they perceive competence or when they perceive incompetence.

\cite{wang2005evaluating} present a widely cited `model' for evaluating the accessibility of information on government websites. This is an important paper with which we should be familiar at a very detailed level as we use archived web content to assess the volume/accessibility of information provided by local governments.

\cite{osman2014cobra} is less relevant, but they develop a multi-item measure to predict the level of citizen satisfaction with e-government services.

\cite{grimmelikhuijsen2012developing} conduct an enormously relevant study. Insofar as we analyze what predicts openness of government websites, we will be replicating and building upon this study. They focus on Dutch municipal websites, and their approach is fairly limited in scope and highly manual (which we can compliment). For example, one of the dependent variables ``Decision-making transparency,'' is measured ``using a discrete (1/0) indicator for whether the underlying principles or reasons for local air pollution policies were given on the Web site.''

\textbf{Why does the content of city websites matter?} According to \cite{Mayhew1974}, politicians engage in advertising, credit claiming and position taking in order to get re-elected. Official city websites allow mayors to do all three. Their offices frequently take a prominent position on the frontpage, and many websites also feature a picture of the candidate. In local politics, where campaign funds are low, this lends the incumbent a crucial advantage in becoming more well-known among her constituents. Furthermore, municipal politics gives incumbents clear and tangible achievements they can point to, such as completed infrastructure projects, the acquisition of federal or state funding, or the hosting of city-wide events. City websites present an opportunity for local officials to brandish these accomplishments. Finally, they also give mayors a platform from which they can advertise their political beliefs. On municipal websites, this may not manifest in the form of brazen partisanship, but more subtle avenues are available. As noted by \cite{einstein2016mayors}, there are stark differences in the spending preferences of Democratic and Republican mayors. City websites can then be used to communicate the stance of a mayor on social or economic programs. Another advantage of websites with regard to communication is that unlike direct social interactions, officials have full control over them.

@@

There doesn't seem to be much literature on transitions of party control, if anything, that question is mostly phrased with regard to political representation. However, if we want to tie our paper to a larger theory, we could go with dynamic representation. Under dynamic representation, policy-makers are responsive to trends in citizens opinions, which mainly manifest/become apparent through election results, especially when incumbents are voted out of office. This fits our topic quite well. Also, of the few papers that do exist on the effects of partisan transitions, virtually all use regression discontinuity designs.

\subsection{Data}
The General Services Administration (GSA) maintains all .gov addresses, and provides a complete\footnote{Domains used for testing and internal programs are excluded.} list of all such domains to the public through GitHub\footnote{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}. This list is updated once per month - we rely on the version released on January 16, 2017. The data from the GSA contains the following variables: One, domain name, specifically, the all-uppercase version of domain and top-level domain (for example, 'ABERDEENMD.GOV'). Two, the type of government entity to which the domain is registered, such as city, county, federal agency, etc. Three, for federal agencies, the name is specfied. Finally, the city in which the domain is registered, is noted.

Here, we focus only on cities. As a first step, we use a webdriver-controlled browser (Firefox/Selenium/Geckodriver) to test whether all of the city websites actually work. Of the 2425 domains listed by the GSA as cities, 292 are not accessible. Furthermore, the .gov domain, as registered at the GSA, is frequently not the website a city actually uses. In many cases, these sites redirect to another address, sometimes not a .gov domain (in this case, we simply use this domain). We record these URLs, as they are required to retrieve the images websites stored in the Wayback Machine (WbM).

$T_{1}+\beta_1$

@@

\begin{figure}[!ht]
	\centering
	\caption{Percentage of state population covered.}
	\includegraphics[width=0.9\linewidth,height=0.9\textheight]{figures/coverage_states.pdf}
\end{figure}

@@

\subsection{Topic modeling}
Note: this chapter is mostly a wordy and less coherent version of the above.

We hypothesize that a change in leadership from one party to the other will lead to a change in website content because the two parties have different agendas. Democrats have a predilection towards policies that promote social and economic equality, whereas Republicans like to emphasize small government as well as law and order. Documents uploaded to city websites are expected to be a reflection of these preferences.

The Latent Dirichlet Allocation (LDA) \citep{Blei2003} is the most commonly used topic model. However, it is unable to account for the existence of two parties with very different policy agendas, translating to different preferred topics. There are two types of extensions to the LDA that fit our subject much better - the structural topic model, and the author-topic model.

The structural topic model, developed by \cite{Roberts2016a} allows researchers to model a corpus as a function of metadata associated with its documents. Specifically, topic prevalence (the proportion of a document made up by a topic) and topical content (the rate at which words figure into a topic) are contingent on a set of covariates. In our case, the two most important covariates are (1) city and (2) authoring party (operationalized by whether a document was present before a change of power, or introduced afterwards). Furthermore, the population size of the city should be a predictor for both the number and kind of problems it faces, which thus need to be addressed on its website. Furthermore, city size also serves as an estimate for the budget and technical capacities of its staff in charge of maintaining the website\footnote{Although this relationship is not exactly deterministic - when looking through .gov websites manually, I've noticed that a lot of websites of (presumably wealthy)  towns of only a few thousand citizens often have extremely well-kept websites}.  Further demographic as well as economic data might also be useful to differentiate cities from one another. If we model the differences between cities properly, we might not have to/should not include city as a (categorical) variable, because it would probably interfere with these more meaningful covariates.

The author-topic model \citep{Rosen-Zvi2004} would allow us to capture the fact that different authors have different topical preferences. Unfortunately, we have two types of 'authors' - cities, and parties. Given the largely divergent administrative needs of different types of cities, we would likely have to treat cities as the author. This would require us to capture the partisan authorship of different documents entirely on the basis of sub-sets of the website data - changed, added, or deleted documents. (Note: In the papers on author-topic models, the intention is often to analyze scientific articles. These articles are often co-authored. Would it be possible to have BOTH cities and parties as authors, so that a specific version of a website would then be 'co-authored' by its city and party?)

The critical element in this analysis is to accurately attribute authorship of documents to either party. Despite possible changes to websites due to a leadership transition, large parts of the content carry over. This means that unless the successor government decides to delete everything, some of the existing documents will be preserved, and in the model, also attributed to the new 'author'. But the reverse is not possible, because the predecessor government can't choose to retain documents from the future. {\em  This is a very important point for municipal websites. We should investigate the possibility of modeling only the changes---documents that change, documents that are deleted, and documents that are added. }

Labeling newly added documents after a change of power is quite simple. As far as older documents are concerned, we would have to operate under the assumption that the incumbent didn't keep his or her successor's document's on the website for four years.\footnote{Probably a safe assumption. However, we could, and probably should test how long documents tend to stay on a city website. Simple descriptive statistics (for example density plots) on the length of existance should likely be sufficient. If we want to be really fancy about it, we could create a duration model, with document topics as features. This would allow us to measure whether some documents tend to remain longer based on their topic (i.e. fire regulations are probably going to stay up longer than notes on a specific council meeting).} One problem here is the fact that the incumbent would have all the administrative topics assigned to them, simply because they have to have those on their website.

If we really do end up getting swamped with administrative terms in our topic models (and it does kind of look like that at the moment), we might be able to separate the signal from the noise by running a preparatory LDA once and using its results to create a new, corpus-specific list of stop words. After that, we run the actual model. This way, politically charged terms and topics, which likely are not as common, but present nevertheless, should be able to rise to the surface. It might be possible to refine this process by running an exploratory model on website data from cities in which party control never changes, and the incumbent always wins by large margins. 'Safe' cities like this should have fairly homogeneous populations, with little need for the incumbent to play politics on the municipal website. Hence, these websites should be filled with purely administrative content.

The use of asymmetric priors \citep{Wallach2009} over the document topic distribution - i.e. the assumption that some topics, such as administrative content, are inherently more common - may be a more elegant way of dealing with this issue.

Another intervening factor is that for cities in Indiana, mayoral terms begin in January. Since a lot of clerical and administrative tasks tend to be year-specific, work tends to pile up around the new year. Thus it is possible that a spike in newly added documents is not due to a change in party control, but owed to a seasonal increase in activity. We can test for this by comparing election years to non-election years. Furthermore, since in Louisiana, mayors take office in May, we have another point of comparison.

Furthermore, if we only investigate cities in which control of government changes from one party to another, we may overestimate its effect. Not only does a transition in party control occur, but the person in charge also changes. Parties are fairly homogeneous, so that two mayors from the same party may have very different policy preferences and managerial styles. To remedy this problem, we [could] utilize matching, pairing our cases with similar cities in which the incumbent does not run for re-election, but party control stays the same nevertheless.

%Justicifcation for Arun 2010 topic number measure
In order to determine the optimal number of topics for our corpus, we utilize the measure developed by \cite{Arun2010}. In contrast to other approaches such as \cite{Cao2009} or \cite{Griffith2004}, this measure includes as much information about the model as possible by taking into account both the document-term matrix, as well as the word-topic matrix. We find 200 topics to be the best value (see figure \ref{ldatuning}).

%One solution might be to rely on LDA models, but only to apply them to documents that were deleted, the strongest possible expression of a successor governments diverging policy preferences. This way, we could identify directly which issues are considered to be the most divisive.

%There is also a possibility that city size is a determinant of the number of topics. Larger cities tend to have bigger websites, owing to a larger set of issues that need to be dealt with.

%Traditional author models that rely on lexical or syntactic differences may also be of use. Parties and their voters are associated with specific educational backgrounds, which may in turn be associated with specific writing styles. However, it seems likely that personal rather than partisan authorship is playing an even larger role here.

%another feasible way of modeling the way in which websites receive a makeover when party control of the mayorship changes. As noted by \citep{Rosen-Zvi2004}, LDA can be considered a special case of the author-topic model, ''where each document has one unique author''. Here, a city website would be a collection of documents, each of which originates entirely from either Democratic or Republican leadership. In a way, this captures the data-generating process more closely.

%Even so, neither the author-topic model nor the LDA model are a perfect fit for the structure of city government websites. One assumes that multiple authors write one document. This may be appropriate for the original purpose of author-topic models, scientific papers, which have multiple authors. This is not as good of a fit for city governments however. Using the LDA instead deals with this problem, but it also assumes that one document has multiple topics. For city government websites, this may be an erroneous assumption, because in many cases, each of these files appears to have one very specific purpose - agricultural, parks and recreation, smoke detectors, and so on.+

%\footnote{This may be wrong in some cases, as they might be leftovers from yet another predecessor government. If the WaybackMachine data reaches back far enough, we might be able to identify and include only the documents that were added since the previous election.}, and the new documents as stemming from party 2. The number of topics \textit{j} would be set to at least three, where one topic would (hopefully) be reserved for purely administrative, non-partisan issues so that the other two (or more) would resolve to party-specific policy issues. Ideally, the result would then show significant differences in the probabilities of authors being assigned to partisan topics.

\begin{figure}[!ht]
	\centering
	\caption{Dates of Wayback Machine snapshots. The vertical lines are municipal elections.}
	\label{snapshots}
	\includegraphics[width=\linewidth]{figures/Snapshots.pdf}
\end{figure}

\begin{figure}[!ht]
	\centering
	%\caption{Population coverage}
	\includegraphics[width=\linewidth]{figures/wtp_current.pdf}
\end{figure}

\begin{figure}[!ht]
	\centering
	%\caption{Population coverage}
	\includegraphics[width=\linewidth]{figures/wtp_current_dem_rep.pdf}
\end{figure}

%\begin{figure}[!ht]
%	\centering
	%\caption{Population coverage}
%	\includegraphics[width=\linewidth]{figures/wtp_before.pdf}
%\end{figure}

%\begin{figure}[!ht]
%	\centering
	%\caption{Population coverage}
%	\includegraphics[width=\linewidth]{figures/wtp_after.pdf}
%\end{figure}

\begin{figure}[!ht]
	\centering
	%\caption{Population coverage}
	\includegraphics[width=\linewidth]{figures/wtp_current_dem_rep_order.pdf}
\end{figure}

%topicweights density
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Densities of topic weights for documents in Republican and Democratic cities (Indiana).}
	\label{doctopics_density}
	\includegraphics[width=\linewidth]{figures/doctopics_density_IN.pdf}
\end{figure}

\subsubsection{LDA diagnostics}

Figure \ref{doctopics_density} plots the densities of topic weights across documents, where each line represents a topic. Distributions with lower peaks near zero and flatter bodies indicate a topic that is present to varying degrees in multiple documents. This shape appears to be more common in documents from Republican cities. By contrast, a distribution with a high peak near zero and a very long tail is indicative of a topic that only appears in one specific document. This appears to be more common for documents in Democratic cities. The substantive conclusion then is that Democrats appear to be more prone to dedicating individual documents to one specific purpose, whereas Republicans produce general-purpose documents more often.

%topicweights density
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Densities of topic weights for documents in Republican and Democratic cities (Indiana).}
	\label{topicweights_density}
	\includegraphics[width=\linewidth]{figures/topicweights_density_IN.pdf}
\end{figure}

An alternative way to consider topic weights is to aggregate them across documents, in this case through their median or mean. Figure \ref{topicweights_density} shows this distribution of topic weights across topics. Most topics have a very low weight - meaning that they do not appear in a lot of documents. When aggregating across documents via the mean, this effect is more pronounced for Republicans, suggesting that most topics do not feature frequently (or even at all) in their documents. Democrats on the other hand appear to have a wider spectrum of topics from which they chose - supporting the hypothesis of Democrats as a 'big tent' party. However, this effect is reversed when using the median instead of the mean to aggregate across documents. Now, the the distribution has a higher peak and lower tail for Democrats. The cause for this stark divergence appears to lie in the fact the mean and median differ enormously - for the range displayed here, the mean is about a hundred times greater. Evidently, extremely large weights (i.e. some documents fitting specific topics perfectly) distort the picture. The median document is a better representation of the corpus as a whole, but the results do not fit our hypothesis. Their are however more consistent with figure \ref{topicweights_density}.

Topics for which there are stark differences in their distribution across documents between Democrats and Republicans are of particular interest to us. To detect these topics, we take the absolute difference of the median document topic weights, and arrange them as a histogram, see figure \ref{diffsize}. For the most part, differences are small. For a few topics however, a contrasts emerges.

%size of the differences
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Word-topic probabilities for topics with big partisan differences (Indiana).}
	\label{diffsize}
	\includegraphics[width=\linewidth]{figures/diffsize_IN.pdf}
\end{figure}

Figure \ref{plotWTP_bigdiffs} displays the word-topic probabilities for the 10 topics with the largest partisan differences. Some of these, such as topic 82, with its focus on policing, safety and crime could be construed as politically charged. For the most part however, these topics focus on administrative matters.

%word topic probabilities for topics with big differences
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Word-topic probabilities for topics with big partisan differences}
	\label{plotWTP_bigdiffs}
	\includegraphics[width=\linewidth]{figures/plotWTP_bigdiffs_IN.pdf}
\end{figure}

To further investigate the topics with large partisan differences, figure \ref{plotWTP_bigdiffs} shows densities of topic weights just like figure \ref{doctopics_density}, but reduced to only the topics with the largest differences. It appears that mere absolute differences between the medians (or some other measure of central tendency) obscures the fact that the distributions themselves are quite different.

%word topic probabilities for topics with big differences
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Word-topic probabilities for topics with big partisan differences}
	\label{doctopics_density_bigdiffs}
	\includegraphics[width=\linewidth]{figures/doctopics_density_bigdiffs_IN.pdf}
\end{figure}

To further investigate this issue, we look at the raw data itself - the document-topic matrices for Democrats and Republicans, displayed as heatmaps. Figure \ref{heatmaps_weights} shows that especially for Republicans (but also for Democrats, to a lesser extent), there appears to be extensive clustering for consecutive documents. Since the order of the documents in the corpus is dependent on the cities in which they appear in, it seems that topics are mere representation of city websites - each website `owns' a number of topics, that appear across all of its documents, and hardly anywhere else. One possible cause for this type of clustering is the fact that documents frequently share common words, for example pertaining to navigation on the site, or standard forms that are shared throughout all documents.

@@

%Heatmaps
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana).}
	\label{heatmaps_weights}
	\includegraphics[width=\linewidth]{figures/heatmaps_weights_IN.png}
\end{figure}

%Heatmaps with no duplicate line removal (threshold set at 999999999)
%also, since the duplicate line removal didn't get rid of as much crap,
%it was necessary to remove non [A-Za-z] characters before hunspell
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana). No duplicate line removal.}
	\label{heatmaps_weights}
	%\includegraphics[width=\linewidth]{figures/heatmaps_weights_noDuplicateRemoval_IN.png}
\end{figure}

%Number of topics vs. tophic coherence
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Topic coherence, varying the number of topics. The red line represents the mean topic coherence for each number of topics.}
	\label{numtopics_coherence}
	\includegraphics[width=\linewidth]{figures/coherence_numberoftopics.pdf}
\end{figure}

%Indiana map
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Cities in the corpus, by partisanship of mayor.}
	\label{indiana_map}
	\includegraphics[height=0.75\textheight]{figures/indiana_map.pdf}
\end{figure}

%partisan topics
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{The most partisan topics. The number in parenthesis indicates how many times more the topic appears on average (measured through the number of words of the topic throughout the documents) in the respective party's corpus (indicated by the color).}
	\label{partisan_topics}
	\includegraphics[height=0.75\textheight]{figures/partisanTopics.pdf}
\end{figure}

%ldatuning
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{The optimal number of topics for our corpus. The measures of Griffths 2004 and Cao 2009 indicate the best number of topics at their minimum, whereas the measure of Arun 2010 points to the best value at its maximum.}
	\label{ldatuning}
	\includegraphics[height=0.75\textheight]{figures/topicnumber_ldatuning.pdf}
\end{figure}

%stm results
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Results from a structural topic model, displayed as the p-values for each variable for each topic. This would normally be somewhat nonsensical, but here it illustrates why the model does not work.}
	\label{stm_results}
%	\includegraphics[width=1.1\linewidth]{figures/stm_results.pdf}
\end{figure}

%fightin words results
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Top democratic and Republican words (Indiana), according to the informed Dirichlet model of Monroe et al. (2008). Ordering is top to bottom for Democrats, and vice versa for Republicans.}
	\label{fightinwordsIN}
	\includegraphics[width=\linewidth]{figures/fightinWordsIN.png}
\end{figure}

%fightin words results
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Top democratic and Republican words (Louisiana), according to the informed Dirichlet model of Monroe et al. (2008). Ordering is top to bottom for Democrats, and vice versa for Republicans.}
	\label{fightinwordsLA}
	\includegraphics[width=\linewidth]{figures/fightinWordsLA.png}
\end{figure}

@@

%fightin words results
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Total number of lines retained at a given threshold for removing duplicated lines. For example, at x = 10, all lines occurring more than 10 times within a city's documents are removed.}
	\label{linesCutoff}
	\includegraphics[width=\linewidth]{figures/linesCutoffIN.pdf}
\end{figure}

%Clustering
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Hierarchical clustering (Indiana).}
	\label{hclustIN}
	\includegraphics[width=\linewidth]{figures/clusteringIN.png}
\end{figure}

%Clustering
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Hierarchical clustering (Louisiana).}
	\label{hclustLA}
	\includegraphics[width=\linewidth]{figures/clusteringLA.png}
\end{figure}

%Entropy by cutoff
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Entropy (between cities, for each topic).}
	\label{cutoffEntropy}
	\includegraphics[width=\linewidth]{figures/CutoffCityEntropy.pdf}
\end{figure}

%Weighted entropy by cutoff
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Weighted (multiplied by tokens assigned to the topic) entropy (between cities, for each topic).}
	\label{cutoffEntropy}
	%\includegraphics[width=\linewidth]{figures/CutoffCityEntropyWeighted.pdf}
\end{figure}

%Clustering
\begin{figure}[!ht]
	\centering
	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
	\label{hclustCity10}
	\includegraphics[width=\linewidth]{figures/heatmap_hclust_10.png}
\end{figure}

%Clustering
\begin{figure}[!ht]
	\centering
	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
	\label{hclustCity20}
	\includegraphics[width=\linewidth]{figures/heatmap_hclust_20.png}
\end{figure}

%Clustering
\begin{figure}[!ht]
	\centering
	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
	\label{hclustCity30}
	\includegraphics[width=\linewidth]{figures/heatmap_hclust_30.png}
\end{figure}

%Clustering
\begin{figure}[!ht]
	\centering
	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
	\label{hclustCity40}
	\includegraphics[width=\linewidth]{figures/heatmap_hclust_40.png}
\end{figure}

%Clustering
\begin{figure}[!ht]
	\centering
	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
	\label{hclustCity50}
	\includegraphics[width=\linewidth]{figures/heatmap_hclust_50.png}
\end{figure}

%Clustering
\begin{figure}[!ht]
	\centering
	\caption{Log number of city documents per cluster. Brighter tile colors indicate more documents. The color of the tile border indicates the city's party.}
	\label{hclustCity100}
	\includegraphics[height = 1.2\textheight]{figures/heatmap_hclust_100.png}
\end{figure}

@@

>>>>

A local government's website is a standard and general source of information for citizens and other community stakeholders. Accordingly, government websites have become prominent sources of data for a variety of research agendas in public administration, public policy, and political science. Existing research has relied on manual methods of website data collection and processing. Reliance on manual collection and processing limits the scale and scope of website content analysis.  We develop a methodological pipeline that researchers can follow in order to gather, process, and analyze website content with established text analysis techniques. First, for the acquisition of website data, we cover approaches to automated scraping methods. Second, pre-processing is a particularly vital step in text analysis, but when websites are concerned, additional measures need to be taken in order to guard against potential sources of bias. We propose a new method for dealing with the kind of duplicated content that is commonly found in government websites. Finally, we illustrate methods of text analysis using automatically gathered and pre-processed website content. We illustrate our methodological pipeline through a new and innovative dataset---the websites of municipal governments in Indiana and Louisiana. We build upon recent research that analyzes how change and variation in the partisan control of government relates to content made available on the government's website. We explore the association between mayoral partisanship and the content of city websites.
%\noindent We explore the effect of transitions of power in municipal governments on the content of their websites. We hypothesize that when party control changes, city administrators modify the contents of their websites in order to fit the agenda of the new incumbent. To test this theory, we study cities in Indiana and Louisiana, two states in which all municipal elections are partisan and the parties of the candidates appear on the ballots. Snapshots of websites before and after transitions of power are acquired through the Wayback Machine. We apply statistical topic models based in latent dirichlet allocation, focusing on changes to the websites. We present results on both which topics see the greatest degree of change associated with transitions in city administrations, and how the topics modified differ with regard to political parties.

@@

\section{The Significance of Government Website Content}
% \cite{grimmelikhuijsen2012developing} conduct an enormously relevant study. Insofar as we analyze what predicts openness of government websites, we will be replicating and building upon this study. They focus on Dutch municipal websites, and their approach is fairly limited in scope and highly manual (which we can compliment). For example, one of the dependent variables ``Decision-making transparency,'' is measured ``using a discrete (1/0) indicator for whether the underlying principles or reasons for local air pollution policies were given on the Web site.''

 According to \cite{Mayhew1974}, politicians engage in advertising, credit claiming and position taking in order to get re-elected. Official city websites allow mayors to do all three. Their offices frequently take a prominent position on the frontpage, and many websites also feature a picture of the candidate. In local politics, where campaign funds are low, this lends the incumbent a crucial advantage in becoming more well-known among her constituents. Furthermore, municipal politics gives incumbents clear and tangible achievements they can point to, such as completed infrastructure projects, the acquisition of federal or state funding, or the hosting of city-wide events. City websites present an opportunity for local officials to brandish these accomplishments. Finally, they also give mayors a platform from which they can advertise their political beliefs. On municipal websites, this may not manifest in the form of brazen partisanship, but more subtle avenues are available. As noted by \cite{einstein2016mayors}, there are stark differences in the spending preferences of Democratic and Republican mayors. City websites can then be used to communicate the stance of a mayor on social or economic programs. Another advantage of websites with regard to communication is that unlike direct social interactions, officials have full control over them.

@@

\section{Data}
In this section we introduce the data we use in our application---the analysis of municipal websites in Louisiana and Indiana. The General Services Administration (GSA) maintains all .gov addresses, and provides a complete\footnote{Domains used for testing and internal programs are excluded.} list of all such domains to the public through GitHub\footnote{https://github.com/GSA/data/tree/gh-pages/dotgov-domains}. This list is updated once per month - we rely on the version released on January 16, 2017. The data from the GSA contains the following variables: One, domain name, specifically, the all-uppercase version of domain and top-level domain (for example, 'ABERDEENMD.GOV'). Two, the type of government entity to which the domain is registered, such as city, county, federal agency, etc. Three, for federal agencies, the name is specfied. Finally, the city in which the domain is registered, is noted.

Here, we focus only on cities. As a first step, we use a webdriver-controlled browser (Firefox/Selenium/Geckodriver) to test whether all of the city websites actually work. Of the 2425 domains listed by the GSA as cities, 292 are not accessible. Furthermore, the .gov domain, as registered at the GSA, is frequently not the website a city actually uses. In many cases, these sites redirect to another address, sometimes not a .gov domain (in this case, we simply use this domain). We record these URLs.

@@

@@

We illustrate the analysis of municipal website content using bag-of-words (BoW) methods. BoW methods are methods of text analysis that do not take into account the sequence or placement of words in text---just the presence and frequency of words.

@@

%Heatmaps
\begin{figure}[htp]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Word-topic probabilities for topics with big partisan differences, across documents (Indiana).}
	\label{heatmaps_weights}
	\includegraphics[width=0.8\linewidth]{figures/heatmaps_weights_IN.png}
\end{figure}

%Indiana map
\begin{figure}[htp]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Cities in the corpus, by partisanship of mayor.}
	\label{indiana_map}
	\includegraphics[height=0.75\textheight]{figures/indiana_map.pdf}
\end{figure}

%stm results
\begin{figure}[htp]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Results from a structural topic model, displayed as the p-values for each variable for each topic. This would normally be somewhat nonsensical, but here it illustrates why the model does not work.}
	\label{stm_results}
%	\includegraphics[width=1.1\linewidth]{figures/stm_results.pdf}
\end{figure}

@@

%fightin words results
\begin{figure}[htp]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\includegraphics[width=\linewidth]{figures/linesCutoffIN.pdf}
		\caption{Total number of lines retained at a given threshold for removing duplicated lines. For example, at x = 10, all lines occurring more than 10 times within a city's documents are removed.}
	\label{linesCutoff}
\end{figure}

@@

\begin{figure}[htp]
	\centering
	\caption{Percentage of state population covered.}
	\includegraphics[width=0.9\linewidth,height=0.9\textheight]{figures/coverage_states.pdf}
\end{figure}
